---
title: "UN Migration Data"
author: "Winnie Hu"
date: "4/22/2020"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: show
always_allow_html: yes
autosize: True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
library(formattable)
library(ggplot2)
library(DT)
library(dplyr)
library(tidyr)
library(scales)
library(tibble)
library(networkD3)
library(visNetwork)
library(tidyverse)
library(xlsx)
```

# Load Data

```{r q_regional_data, echo=TRUE}
#setwd("C:/Users/Winnie/Documents/NeilJohnson/Migration/Version_9_April_7")
nodes <- read.csv("CountryNodes_All.csv", header=T, as.is=T)
links <- read.csv("EdgeList_All.csv", header=T, as.is=T)
nodes
links
nrow(links[links$flow2019 > 0, ])
```

# Figure 1: Time Series Plots from 2005 to 2019 focusing on top 100 migration corridors

### i) Create links dataframes

```{r q_plot_2_link, echo=TRUE}
## 2019
linkcols19 <- c("Origin", "Destination", "flow2019")
links19 <- links[linkcols19]
links19_sort <- links19[order(-links19$flow2019),] # sort the dataframe by migration flow in 2019
top_X_corridors_19 <- links19_sort[1:100,]  # get the top 100 migration corridors

## 2015
linkcols15 <- c("Origin", "Destination", "flow2015")
links15 <- links[linkcols15]
links15_sort <- links15[order(-links15$flow2015),] 
top_X_corridors_15 <- links15_sort[1:100,] 

## 2010
linkcols10 <- c("Origin", "Destination", "flow2010")
links10 <- links[linkcols10]
links10_sort <- links10[order(-links10$flow2010),] 
top_X_corridors_10 <- links10_sort[1:100,]

## 2005
linkcols05 <- c("Origin", "Destination", "flow2005")
links05 <- links[linkcols05]
links05_sort <- links05[order(-links05$flow2005),] 
top_X_corridors_05 <- links05_sort[1:100,] 
```

### ii) Create nodes dataframes

```{r q_plot_3_node, echo=TRUE}
### 2019
# show only nodes that appear in the top_X_corridors_19 dataframe
# get the disctinct countries that appear in top_X_corridors_19
destination19_set <- unique(top_X_corridors_19$Destination)
origin19_set <- unique(top_X_corridors_19$Origin)
union19_set <- union(destination19_set, origin19_set) # get the union of both vector

# select rows from the nodes dataframe that contain only length(union19_set) countries
nodecols19 <- c("Country", "Country", "Region", "UN_Region", "Influenza2019")
nodes19 <- nodes[nodecols19]
names(nodes19)[2] <- "Label"  # rename "Country.1" to "Label"
nodes19 <- nodes19[nodes19$Country %in% union19_set, ]

### create a variable that saves the total number of immigrants to a destination country
num_immigrants_19 <- aggregate(top_X_corridors_19$flow2019, by = list(Category = top_X_corridors_19$Destination), FUN=sum)
names(num_immigrants_19)[names(num_immigrants_19) == "x"] <- "Total_New_Immigrants_19"  # change column name 

# add new rows
setdiff19 <- setdiff(origin19_set, destination19_set)
zero_immigrants_19 <- rep(0, length(setdiff19))
df_new_19 <- data.frame(Category = setdiff19, Total_New_Immigrants_19 = zero_immigrants_19)
num_immigrants_19 <- rbind(num_immigrants_19, df_new_19)
names(num_immigrants_19)[names(num_immigrants_19) == "Category"] <- "Country"
# join two dfs tgt
nodes19 <- merge(nodes19, num_immigrants_19, by = "Country")
nodes19



### 2015
# show only nodes that appear in the top_100_corridors_15 dataframe
# get the disctinct country that appear in top_100_corridors_15
destination15_set <- unique(top_X_corridors_15$Destination)
origin15_set <- unique(top_X_corridors_15$Origin)
union15_set <- union(destination15_set, origin15_set) # get the union of both vector

# select rows from the nodes dataframe that contain only length(union15_set) countries
nodecols15 <- c("Country", "Country", "Region", "UN_Region", "Influenza2015")
nodes15 <- nodes[nodecols15]
names(nodes15)[2] <- "Label"  # rename "Country.1" to "Label"
nodes15 <- nodes15[nodes15$Country %in% union15_set, ]

### create a variable that saves the total number of immigrants to a destination country
num_immigrants_15 <- aggregate(top_X_corridors_15$flow2015, by = list(Category = top_X_corridors_15$Destination), FUN=sum)
names(num_immigrants_15)[names(num_immigrants_15) == "x"] <- "Total_New_Immigrants_15"  # change column name

# add new rows
setdiff15 <- setdiff(origin15_set, destination15_set)
zero_immigrants_15 <- rep(0, length(setdiff15))
df_new_15 <- data.frame(Category = setdiff15, Total_New_Immigrants_15 = zero_immigrants_15)
num_immigrants_15 <- rbind(num_immigrants_15, df_new_15)
names(num_immigrants_15)[names(num_immigrants_15) == "Category"] <- "Country"
nodes15 <- merge(nodes15, num_immigrants_15, by = "Country") # join two dfs tgt
nodes15



### 2010
# show only nodes that appear in the top_100_corridors_10 dataframe
# get the disctinct country that appear in top_100_corridors_10
destination10_set <- unique(top_X_corridors_10$Destination)
origin10_set <- unique(top_X_corridors_10$Origin)
union10_set <- union(destination10_set, origin10_set) # get the union of both vector

# select rows from the nodes dataframe that contain only length(union10_set) countries
nodecols10 <- c("Country", "Country", "Region", "UN_Region", "Influenza2010")
nodes10 <- nodes[nodecols10]
names(nodes10)[2] <- "Label"  # rename "Country.1" to "Label"
nodes10 <- nodes10[nodes10$Country %in% union10_set, ]

### create a variable that saves the total number of immigrants to a destination country
num_immigrants_10 <- aggregate(top_X_corridors_10$flow2010, by = list(Category = top_X_corridors_10$Destination), FUN=sum)
names(num_immigrants_10)[names(num_immigrants_10) == "x"] <- "Total_New_Immigrants_10"  # change column name

# add new rows
setdiff10 <- setdiff(origin10_set, destination10_set)
zero_immigrants_10 <- rep(0, length(setdiff10))
df_new_10 <- data.frame(Category = setdiff10, Total_New_Immigrants_10 = zero_immigrants_10)
num_immigrants_10 <- rbind(num_immigrants_10, df_new_10)
names(num_immigrants_10)[names(num_immigrants_10) == "Category"] <- "Country"
nodes10 <- merge(nodes10, num_immigrants_10, by = "Country") # join two dfs tgt
nodes10



### 2005
# show only nodes that appear in the top_100_corridors_05 dataframe
# get the disctinct country that appear in top_100_corridors_05
destination05_set <- unique(top_X_corridors_05$Destination)
origin05_set <- unique(top_X_corridors_05$Origin)
union05_set <- union(destination05_set, origin05_set) # get the union of both vector

# select rows from the nodes dataframe that contain only length(union05_set) countries
nodecols05 <- c("Country", "Country", "Region", "UN_Region", "Influenza2005")
nodes05 <- nodes[nodecols05]
names(nodes05)[2] <- "Label"  # rename "Country.1" to "Label"
nodes05 <- nodes05[nodes05$Country %in% union05_set, ]

### create a variable that saves the total number of immigrants to a destination country
num_immigrants_05 <- aggregate(top_X_corridors_05$flow2005, by = list(Category = top_X_corridors_05$Destination), FUN=sum)
names(num_immigrants_05)[names(num_immigrants_05) == "x"] <- "Total_New_Immigrants_05"  # change column name 

# add new rows
setdiff05 <- setdiff(origin05_set, destination05_set)
zero_immigrants_05 <- rep(0, length(setdiff05))
df_new_05 <- data.frame(Category = setdiff05, Total_New_Immigrants_05 = zero_immigrants_05)
num_immigrants_05 <- rbind(num_immigrants_05, df_new_05)
names(num_immigrants_05)[names(num_immigrants_05) == "Category"] <- "Country"
#num_immigrants_05
#nrow(num_immigrants_05)
nodes05 <- merge(nodes05, num_immigrants_05, by = "Country") # join two dfs tgt
nodes05
```

### iii) rescale nodes dataframes

```{r q_plot_3_rescale_nodes, echo=FALSE}
# find out the min and max across all four years' data
min_TNI_19 <- min(nodes19$Total_New_Immigrants_19)
min_TNI_15 <- min(nodes15$Total_New_Immigrants_15)
min_TNI_10 <- min(nodes10$Total_New_Immigrants_10)
min_TNI_05 <- min(nodes05$Total_New_Immigrants_05)
min_TNI_all <- min(c(min_TNI_19, min_TNI_15, min_TNI_10, min_TNI_05))
min_TNI_all

max_TNI_19 <- max(nodes19$Total_New_Immigrants_19)
max_TNI_15 <- max(nodes15$Total_New_Immigrants_15)
max_TNI_10 <- max(nodes10$Total_New_Immigrants_10)
max_TNI_05 <- max(nodes05$Total_New_Immigrants_05)
max_TNI_all <- max(c(max_TNI_19, max_TNI_15, max_TNI_10, max_TNI_05))
max_TNI_all

# rescale total new immigrants data
# 2019
nodes19$Rescale_TNI2019 <- rescale(x = nodes19$Total_New_Immigrants_19, to = c(4, 26), from = c(min_TNI_all, max_TNI_all), na.rm = TRUE, finite = TRUE)
# 2015
nodes15$Rescale_TNI2015 <- rescale(x = nodes15$Total_New_Immigrants_15, to = c(4, 26), from = c(min_TNI_all, max_TNI_all), na.rm = TRUE, finite = TRUE)
# 2010
nodes10$Rescale_TNI2010 <- rescale(x = nodes10$Total_New_Immigrants_10, to = c(4, 26), from = c(min_TNI_all, max_TNI_all), na.rm = TRUE, finite = TRUE)
# 2005
nodes05$Rescale_TNI2005 <- rescale(x = nodes05$Total_New_Immigrants_05, to = c(4, 26), from = c(min_TNI_all, max_TNI_all), na.rm = TRUE, finite = TRUE)
```

### iv) rescale links dataframes

```{r q_plot_3_rescale_links, echo=FALSE}
# find out the min and max across all four years' data
#links
min_mf_19 <- min(top_X_corridors_19$flow2019)
min_mf_15 <- min(top_X_corridors_15$flow2015)
min_mf_10 <- min(top_X_corridors_10$flow2010)
min_mf_05 <- min(top_X_corridors_05$flow2005)
min_all_mf <- min(c(min_mf_19, min_mf_15, min_mf_10, min_mf_05))
min_all_mf

max_mf_19 <- max(top_X_corridors_19$flow2019)
max_mf_15 <- max(top_X_corridors_15$flow2015)
max_mf_10 <- max(top_X_corridors_10$flow2010)
max_mf_05 <- max(top_X_corridors_05$flow2005)
max_all_mf <- max(c(max_mf_19, max_mf_15, max_mf_10, max_mf_05))
max_all_mf

# rescale all migration flow data
#2019
top_X_corridors_19$Rescale_MF_19 <- rescale(x = top_X_corridors_19$flow2019, to = c(0.4, 4), from = c(min_all_mf, max_all_mf), na.rm = TRUE, finite = TRUE)
#2015
top_X_corridors_15$Rescale_MF_15 <- rescale(x = top_X_corridors_15$flow2015, to = c(0.4, 4), from = c(min_all_mf, max_all_mf), na.rm = TRUE, finite = TRUE)
#2010
top_X_corridors_10$Rescale_MF_10 <- rescale(x = top_X_corridors_10$flow2010, to = c(0.4, 4), from = c(min_all_mf, max_all_mf), na.rm = TRUE, finite = TRUE)
#2005
top_X_corridors_05$Rescale_MF_05 <- rescale(x = top_X_corridors_05$flow2005, to = c(0.4, 4), from = c(min_all_mf, max_all_mf), na.rm = TRUE, finite = TRUE)
```

```{r q_export, echo=FALSE}
#write.xlsx(nodes19, "nodes19.xlsx")
#write.xlsx(top_X_corridors_19, "links19.xlsx")
```

### v) plot 2019

```{r q_plot_3_19, echo=FALSE}
### Plot from 2005 to 2019
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2019_rescale <- graph_from_data_frame(d = top_X_corridors_19, vertices = nodes19, directed=T) 

# node size (total new immigrants)
V(net_2019_rescale)$size <- V(net_2019_rescale)$Rescale_TNI2019

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.6)
my_color <- colrstr[as.numeric(as.factor(V(net_2019_rescale)$UN_Region))]
V(net_2019_rescale)$color <- my_color
V(net_2019_rescale)$frame.color <- "white"
V(net_2019_rescale)$frame.size <- 0.1

# node label
V(net_2019_rescale)$label.color <- 'black'
V(net_2019_rescale)$label <- V(net_2019_rescale)$Label
V(net_2019_rescale)$label.cex = 0.2

# edge width
E(net_2019_rescale)$width <- E(net_2019_rescale)$Rescale_MF_19


# set arrow size
E(net_2019_rescale)$arrow.size <- 0.1
E(net_2019_rescale)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)
#set.seed(129)

#png("Figure_top100_2019_fr_time_series.png", width=6, height=6, units='in',res=1000)
png("Figure_top100_2019_fr_time_series.png", width=6, height=6, units='in',res=1000)

# plot 2019
#l <- layout_with_fr(net_2019_rescale)
#l <- norm_coords(l, ymin=-1, ymax=1, xmin=-1, xmax=1)

plot(net_2019_rescale, layout = layout_with_fr)
#title("2019: Influenza Cases vs Migration Flow Data (Regional Data) (fr)", cex.main = 1)


# Add a legend
legend("topleft", legend=levels(as.factor(V(net_2019_rescale)$UN_Region)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrs, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()

```

Statistical data analysis

```{r q_plot_2019_EDA, echo=FALSE}
top_X_corridors_19
nodes19

# raw data
# in-flow
top_MF_19 <- aggregate(top_X_corridors_19$flow2019, by=list(Category=top_X_corridors_19$Destination), FUN=sum)
top_MF_19_sort <- top_MF_19[order(-top_MF_19$x),]
colnames(top_MF_19_sort) <- c("Top In-flow Country", "Total Immigrants")
top_MF_19_sort

# out-flow
top_MF_EXP_19 <- aggregate(top_X_corridors_19$flow2019, by=list(Category=top_X_corridors_19$Origin), FUN=sum)
top_MF_EXP_19_sort <- top_MF_EXP_19[order(-top_MF_EXP_19$x),]
colnames(top_MF_EXP_19_sort) <- c("Top Out-flow Country", "Total Emigrants")
top_MF_EXP_19_sort

# rescale data
# in-flow
top_MF_19 <- aggregate(top_X_corridors_19$Rescale_MF_19, by=list(Category=top_X_corridors_19$Destination), FUN=sum)
top_MF_19_sort <- top_MF_19[order(-top_MF_19$x),]
colnames(top_MF_19_sort) <- c("Top In-flow Country", "Total Immigrants (rescaled)")
top_MF_19_sort

# out-flow
top_MF_EXP_19 <- aggregate(top_X_corridors_19$Rescale_MF_19, by=list(Category=top_X_corridors_19$Origin), FUN=sum)
top_MF_EXP_19_sort <- top_MF_EXP_19[order(-top_MF_EXP_19$x),]
colnames(top_MF_EXP_19_sort) <- c("Top Out-flow Country", "Total Emigrants (rescaled)")
top_MF_EXP_19_sort

```


### vi) plot 2015

```{r q_plot_3_15, echo=FALSE}
### Plot from 2005 to 2019
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2015_rescale <- graph_from_data_frame(d = top_X_corridors_15, vertices = nodes15, directed=T) 

# node size (total new immigrants)
V(net_2015_rescale)$size <- V(net_2015_rescale)$Rescale_TNI2015

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.6)
my_color <- colrstr[as.numeric(as.factor(V(net_2015_rescale)$UN_Region))]
V(net_2015_rescale)$color <- my_color
V(net_2015_rescale)$frame.color <- "white"
V(net_2015_rescale)$frame.size <- 0.1

# node label
V(net_2015_rescale)$label.color <- 'black'
V(net_2015_rescale)$label <- V(net_2015_rescale)$Label
V(net_2015_rescale)$label.cex = 0.2

# edge width
E(net_2015_rescale)$width <- E(net_2015_rescale)$Rescale_MF_15


# set arrow size
E(net_2015_rescale)$arrow.size <- 0.1
E(net_2015_rescale)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)

png("Figure_top100_2015_fr_time_series.png", width=6, height=6, units='in',res=1000)

plot(net_2015_rescale, layout = layout_with_fr)
#title("2015: Influenza Cases vs Migration Flow Data (Regional Data) (fr)", cex.main = 1)


# Add a legend
legend("topleft", legend=levels(as.factor(V(net_2015_rescale)$UN_Region)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrs, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()

```

### vii) plot 2010

```{r q_plot_3_10, echo=FALSE}
### Plot from 2005 to 2019
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2010_rescale <- graph_from_data_frame(d = top_X_corridors_10, vertices = nodes10, directed=T) 

# node size (total new immigrants)
V(net_2010_rescale)$size <- V(net_2010_rescale)$Rescale_TNI2010

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.6)
my_color <- colrstr[as.numeric(as.factor(V(net_2010_rescale)$UN_Region))]
V(net_2010_rescale)$color <- my_color
V(net_2010_rescale)$frame.color <- "white"
V(net_2010_rescale)$frame.size <- 0.1

# node label
V(net_2010_rescale)$label.color <- 'black'
V(net_2010_rescale)$label <- V(net_2010_rescale)$Label
V(net_2010_rescale)$label.cex = 0.2

# edge width
E(net_2010_rescale)$width <- E(net_2010_rescale)$Rescale_MF_10


# set arrow size
E(net_2010_rescale)$arrow.size <- 0.1
E(net_2010_rescale)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)

png("Figure_top100_2010_fr_time_series.png", width=6, height=6, units='in',res=1000)

plot(net_2010_rescale, layout = layout_with_fr)
#title("2010: Influenza Cases vs Migration Flow Data (Regional Data) (fr)", cex.main = 1)


# Add a legend
legend("topleft", legend=levels(as.factor(V(net_2010_rescale)$UN_Region)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrs, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()

```

### vii) plot 2005

```{r q_plot_3_05, echo=FALSE}
### Plot from 2005 to 2019
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2005_rescale <- graph_from_data_frame(d = top_X_corridors_05, vertices = nodes05, directed=T) 

# node size (total new immigrants)
V(net_2005_rescale)$size <- V(net_2005_rescale)$Rescale_TNI2005

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.6)
my_color <- colrstr[as.numeric(as.factor(V(net_2005_rescale)$UN_Region))]
V(net_2005_rescale)$color <- my_color
V(net_2005_rescale)$frame.color <- "white"
V(net_2005_rescale)$frame.size <- 0.1

# node label
V(net_2005_rescale)$label.color <- 'black'
V(net_2005_rescale)$label <- V(net_2005_rescale)$Label
V(net_2005_rescale)$label.cex = 0.2

# edge width
E(net_2005_rescale)$width <- E(net_2005_rescale)$Rescale_MF_05


# set arrow size
E(net_2005_rescale)$arrow.size <- 0.1
E(net_2005_rescale)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)

png("Figure_top100_2005_fr_time_series.png", width=6, height=6, units='in',res=1000)

plot(net_2005_rescale, layout = layout_with_fr)
#title("2005: Influenza Cases vs Migration Flow Data (Regional Data) (fr)", cex.main = 1)


# Add a legend
legend("topleft", legend=levels(as.factor(V(net_2005_rescale)$UN_Region)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrs, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()

```

The following section is dedicated to extract statistial data.

```{r q_plot_3_EDA, echo=TRUE}
# 2019
E(net_2019_rescale)$weight <- E(net_2019_rescale)$width
top_ND_19 <- sort(strength(net_2019_rescale, vids = V(net_2019_rescale), mode = "in", loops = TRUE), decreasing = TRUE)
#top_ND_19

top_MF_19 <- aggregate(top_X_corridors_19$flow2019, by=list(Category=top_X_corridors_19$Destination), FUN=sum)
top_MF_19_sort <- top_MF_19[order(-top_MF_19$x),]
top_MF_19_sort

top_MF_19_sum <- sum(top_MF_19_sort$x)
#top_MF_19_sum
links_sum <- sum(links$flow2019)
top_MF_19_sum / links_sum

nrow(nodes19)

# 2015
top_MF_15 <- aggregate(top_X_corridors_15$flow2015, by=list(Category=top_X_corridors_15$Destination), FUN=sum)
top_MF_15_sort <- top_MF_15[order(-top_MF_15$x),]
top_MF_15_sort

top_MF_15_sum <- sum(top_MF_15_sort$x)
#top_MF_19_sum
links_sum <- sum(links$flow2015)
top_MF_15_sum / links_sum

nrow(nodes15)

# 2010
top_MF_10 <- aggregate(top_X_corridors_10$flow2010, by=list(Category=top_X_corridors_10$Destination), FUN=sum)
top_MF_10_sort <- top_MF_10[order(-top_MF_10$x),]
top_MF_10_sort

top_MF_10_sum <- sum(top_MF_10_sort$x)
#top_MF_19_sum
links_sum <- sum(links$flow2010)
top_MF_10_sum / links_sum

nrow(nodes10)

# 2005
top_MF_05 <- aggregate(top_X_corridors_05$flow2005, by=list(Category=top_X_corridors_05$Destination), FUN=sum)
top_MF_05_sort <- top_MF_05[order(-top_MF_05$x),]
top_MF_05_sort

top_MF_05_sum <- sum(top_MF_05_sort$x)
#top_MF_19_sum
links_sum <- sum(links$flow2005)
top_MF_05_sum / links_sum

nrow(nodes05)
```



# Figure 2: Highlight large and small influenza countries (world median as threshold)

### i) Plot 2019

```{r q_plot_4_color_variable, echo=TRUE}
# get the median of the influenza case number
X_pctl <- quantile(nodes$Influenza2019, c(0.5))
X_pctl
# select countries whose influenza case numbers are greater than X_pctl
top_IC_19 <- nodes19[nodes19$Influenza2019 >= X_pctl, ]$Country
non_top_IC_19 <- nodes19[nodes19$Influenza2019 < X_pctl, ]$Country

# assign color labels
nodes19$Node_Color_19 <- "Influenza Cases < World Median Level"
for (val in top_IC_19){
  nodes19[nodes19$Country == val,]$Node_Color_19 <- "Influenza Cases >= World Median Level"
}

# Plot
### Plot from 2005 to 2019
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2019_color <- graph_from_data_frame(d = top_X_corridors_19, vertices = nodes19, directed=T) 

# node size (total new immigrants)
V(net_2019_color)$size <- V(net_2019_color)$Rescale_TNI2019

# node color
colrs  <- c("blue", "red")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_2019_color)$Node_Color_19))]
V(net_2019_color)$color <- my_color
V(net_2019_color)$frame.color <- "white"
V(net_2019_color)$frame.size <- 0.1

# node label
V(net_2019_color)$label.color <- 'black'
V(net_2019_color)$label <- V(net_2019_color)$Label
V(net_2019_color)$label.cex = 0.2

# edge width
E(net_2019_color)$width <- E(net_2019_color)$Rescale_MF_19


# set arrow size
E(net_2019_color)$arrow.size <- 0.1
E(net_2019_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)

png("Figure_top100_2019_fr_influenza_highlights_top050.png", width=6, height=6, units='in',res=1000)


plot(net_2019_color, layout = layout_with_fr)

# Add a legend
legend("topright", legend=levels(as.factor(V(net_2019_color)$Node_Color_19)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrstr, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()
```

### ii) Plot 2015

```{r q_plot_4_color_variable_2015, echo=TRUE}
# get the median of the influenza case number
X_pctl <- quantile(nodes$Influenza2015, c(0.5))
X_pctl
# select countries whose influenza case numbers are greater than X_pctl
top_IC_15 <- nodes15[nodes15$Influenza2015 >= X_pctl, ]$Country
non_top_IC_15 <- nodes15[nodes15$Influenza2015 < X_pctl, ]$Country

# assign color labels
nodes15$Node_Color_15 <- "Influenza Cases < World Median Level"
for (val in top_IC_15){
  nodes15[nodes15$Country == val,]$Node_Color_15 <- "Influenza Cases >= World Median Level"
}

# Plot
### Plot 2015
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2015_color <- graph_from_data_frame(d = top_X_corridors_15, vertices = nodes15, directed=T) 

# node size (total new immigrants)
V(net_2015_color)$size <- V(net_2015_color)$Rescale_TNI2015

# node color
colrs  <- c("blue", "red")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_2015_color)$Node_Color_15))]
V(net_2015_color)$color <- my_color
V(net_2015_color)$frame.color <- "white"
V(net_2015_color)$frame.size <- 0.1

# node label
V(net_2015_color)$label.color <- 'black'
V(net_2015_color)$label <- V(net_2015_color)$Label
V(net_2015_color)$label.cex = 0.2

# edge width
E(net_2015_color)$width <- E(net_2015_color)$Rescale_MF_15


# set arrow size
E(net_2015_color)$arrow.size <- 0.1
E(net_2015_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)

png("Figure_top100_2015_fr_influenza_highlights_top050.png", width=6, height=6, units='in',res=1000)

plot(net_2015_color, layout = layout_with_fr)

# Add a legend
legend("topright", legend=levels(as.factor(V(net_2015_color)$Node_Color_15)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrstr, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()
```

### iii) Plot 2010

```{r q_plot_4_color_variable_2010, echo=TRUE}
# get the median of the influenza case number
X_pctl <- quantile(nodes$Influenza2010, c(0.5))
X_pctl
# select countries whose influenza case numbers are greater than X_pctl
top_IC_10 <- nodes10[nodes10$Influenza2010 >= X_pctl, ]$Country
non_top_IC_10 <- nodes10[nodes10$Influenza2010 < X_pctl, ]$Country

# assign color labels
nodes10$Node_Color_10 <- "Influenza Cases < World Median Level"
for (val in top_IC_10){
  nodes10[nodes10$Country == val,]$Node_Color_10 <- "Influenza Cases >= World Median Level"
}

# Plot
### Plot 2010
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2010_color <- graph_from_data_frame(d = top_X_corridors_10, vertices = nodes10, directed=T) 

# node size (total new immigrants)
V(net_2010_color)$size <- V(net_2010_color)$Rescale_TNI2010

# node color
colrs  <- c("red", "blue")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_2010_color)$Node_Color_10))]
V(net_2010_color)$color <- my_color
V(net_2010_color)$frame.color <- "white"
V(net_2010_color)$frame.size <- 0.1

# node label
V(net_2010_color)$label.color <- 'black'
V(net_2010_color)$label <- V(net_2010_color)$Label
V(net_2010_color)$label.cex = 0.2

# edge width
E(net_2010_color)$width <- E(net_2010_color)$Rescale_MF_10


# set arrow size
E(net_2010_color)$arrow.size <- 0.1
E(net_2010_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)

png("Figure_top100_2010_fr_influenza_highlights_top050.png", width=6, height=6, units='in',res=1000)

plot(net_2010_color, layout = layout_with_fr)

# Add a legend
legend("topright", legend=levels(as.factor(V(net_2010_color)$Node_Color_10)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrstr, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()
```

### iv) Plot 2005

```{r q_plot_4_color_variable_2005, echo=TRUE}
# get the median of the influenza case number
X_pctl <- quantile(nodes$Influenza2005, c(0.5))
X_pctl
# select countries whose influenza case numbers are greater than X_pctl
top_IC_05 <- nodes05[nodes05$Influenza2005 >= X_pctl, ]$Country
non_top_IC_05 <- nodes05[nodes05$Influenza2005 < X_pctl, ]$Country

# assign color labels
nodes05$Node_Color_05 <- "Influenza Cases < World Median Level"
for (val in top_IC_05){
  nodes05[nodes05$Country == val,]$Node_Color_05 <- "Influenza Cases >= World Median Level"
}

# Plot
### Plot from 2005 to 2019
# set figure size
par(pin=c(6, 6))
par(mai=c(0, 0, 0, 0))

net_2005_color <- graph_from_data_frame(d = top_X_corridors_05, vertices = nodes05, directed=T) 

# node size (total new immigrants)
V(net_2005_color)$size <- V(net_2005_color)$Rescale_TNI2005

# node color
colrs  <- c("red", "blue")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_2005_color)$Node_Color_05))]
V(net_2005_color)$color <- my_color
V(net_2005_color)$frame.color <- "white"
V(net_2005_color)$frame.size <- 0.1

# node label
V(net_2005_color)$label.color <- 'black'
V(net_2005_color)$label <- V(net_2005_color)$Label
V(net_2005_color)$label.cex = 0.2

# edge width
E(net_2005_color)$width <- E(net_2005_color)$Rescale_MF_05


# set arrow size
E(net_2005_color)$arrow.size <- 0.1
E(net_2005_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1242)

png("Figure_top100_2005_fr_influenza_highlights_top050.png", width=6, height=6, units='in',res=1000)

plot(net_2005_color, layout = layout_with_fr)

# Add a legend
legend("topright", legend=levels(as.factor(V(net_2005_color)$Node_Color_05)), col = colrstr, bty = "n", pch=16, pt.cex = 0.8, cex = .3, text.col = colrstr, horiz = FALSE, inset = c(0.1, 0.1))

dev.off()
```


# Random Models

### i) Comparing Mean Betweenness Centrality between Null model and Random Model

```{r q_random_model, echo=TRUE}
# get number of vertices and edges for random networks
num_nodes <- length(V(net_2019_rescale))
num_nodes
num_links <- length(E(net_2019_rescale))
num_links

null_betweenness_centrality <- mean(betweenness(net_2019_rescale, v = V(net_2019_rescale), directed = TRUE))
null_betweenness_centrality

null_in_degree <- max(degree(net_2019_rescale, mode = "in"))
null_in_degree

betweenness(net_2019_rescale, directed = TRUE)

# generate random networks using the parameters from the given network
# initialize random dataframe
random_g_matrics <- data.frame()
set.seed(1242)
for (i in 1: 1000){
  g <- sample_gnm(n = num_nodes, m = num_links, directed = TRUE, loops = FALSE)
  random_betweenness_centrality <- mean(betweenness(g, v = V(g), directed = TRUE))
  random_max_in_degree <- max(degree(g, mode = "in"))
  random_matrics <- data.frame(random_betweenness_centrality,
                               random_max_in_degree)
  random_g_matrics <- rbind(random_g_matrics, random_matrics)
}
random_g_matrics

mean_random_bc <- mean(random_g_matrics$random_betweenness_centrality)
mean_random_bc

mean_random_max_in_degree <- mean(random_g_matrics$random_max_in_degree)
mean_random_max_in_degree

h <- hist(random_g_matrics$random_betweenness_centrality,
          main = NA,
          xlab = "Betweenness Centrality",
          col = "grey80",
          border="white",
          breaks = 25)
text(h$mids,h$counts,labels=h$counts, adj=c(0.5, 0))
title("Distribution of Random Networks Mean Betweenness Centrality", line = 0.5)
abline(v = null_betweenness_centrality, col = "red", lty = 3, lwd = 2)
text(30, 28.4, "2.45 (Null Model)", col = 'red')

# color: https://www.r-graph-gallery.com/42-colors-names.html
```

### ii) Comparing Max In-degree between Null model and Random Model

```{r q_random_model_2, echo=TRUE}
#top_X_corridors_19
# indegree
h2 <- hist(random_g_matrics$random_max_in_degree,
          main = NA,
          xlab = "Max In-Degree",
          col = "grey80",
          border="white",
          breaks = 8,
          xlim=c(min(random_g_matrics$random_max_in_degree), null_in_degree + 1))
text(h2$mids,h2$counts,labels=h2$counts, adj=c(0.5, 0))
title("Distribution of Random Networks Node Max In-Degree", line = 0.5)
abline(v = null_in_degree, col = "red", lty = 3, lwd = 2)
text(16, 68.4, "18 (Null Model)", col = 'red')
#axis(side = 1, at=c(min(random_g_matrics$random_max_in_degree), 5, 15, null_in_degree + 1))
axis(side=1, at=seq(min(random_g_matrics$random_max_in_degree), null_in_degree + 1, 1))
```

### iii) Comparing mean betweenness centrality between large influenza countries and small influenza countries using random network

```{r q_random_model_EDA_2_1, echo=TRUE}
# get the country names of big influenza countries and small influenza countries
# These two variables were defined in the color highlights plots
top_IC_19 
non_top_IC_19

# get the mean of the BC of big and small influenza countries
# calculate the BC of top influenza countries
BC_19 <- betweenness(net_2019_color)
mean_BC_BIC <- mean(BC_19[top_IC_19])
mean_BC_BIC
mean_BC_SIC <- mean(BC_19[non_top_IC_19])
mean_BC_SIC

# get the mean of the in-degree of top and small influenza countries
BC_19_ID <- degree(net_2019_color, mode = "in")
mean_ID_BIC <- mean(BC_19_ID[top_IC_19])
mean_ID_BIC
mean_ID_SIC <- mean(BC_19_ID[non_top_IC_19])
mean_ID_SIC

# get the numbers of big/small influenza countries, respectively
num_BIC <- length(top_IC_19)
num_sIC <- length(non_top_IC_19)


# randome networks
# Assumption: the BC of big influenza countries are greater than the BC of small influenza countries
# get number of vertices and edges for random networks
num_nodes <- length(V(net_2019_color))
num_nodes
num_links <- length(E(net_2019_color))
num_links

# get the difference of the mean BC of big countries and small countries, respectively
null_mean_difference_BC <- mean_ID_BIC - mean_ID_SIC

# generate random networks using the parameters from the given network
# initialize random dataframe
random_g_matrics <- data.frame()
set.seed(1242)
for (i in 1: 1000){
  ## run a random network
  g <- sample_gnm(n = num_nodes, m = num_links, directed = TRUE, loops = FALSE)
  ## get the results
  random_betweenness_centrality <- betweenness(g, v = V(g), directed = TRUE)
  random_mean_BC <- mean(random_betweenness_centrality)
  # set the first 59 nodes as big influenza countries
  random_mean_big_BC <- mean(random_betweenness_centrality[1:59]) 
  # set the rest of the nodes as small influenza countries
  random_mean_small_BC <- mean(random_betweenness_centrality[60:74]) 
  random_diff <- random_mean_big_BC - random_mean_small_BC
  ## save the current random neetwork's results into a dataframe
  random_matrics <- data.frame(random_mean_BC,
                               random_mean_big_BC,
                               random_mean_small_BC,
                               random_diff)
  ## combine to previous results
  random_g_matrics <- rbind(random_g_matrics, random_matrics)
}
random_g_matrics

# generate histogram
h <- hist(random_g_matrics$random_diff,
          main = NA,
          xlab = "Betweenness Centrality",
          col = "grey80",
          border="white",
          breaks = 25)
text(h$mids,h$counts,labels=h$counts, adj=c(0.5, 0))
title("Distribution of Mean Difference \nbetween Big Influenza Countries BC and Small Influenza Countries BC", line = 0.5, cex.main = 0.8)
abline(v = null_mean_difference_BC, col = "red", lty = 3, lwd = 2)
text(30, 28.4, "2.45 (Null Model)", col = 'red')
```

### iii) Network Properties - top 10 BC in 2019

```{r q_random_model_EDA_2, echo=TRUE}
# use raw data rather than rescaled data to calculate the BC 
linkcols19 <- c("Destination", "Origin", "flow2019")
links19 <- top_X_corridors_19[linkcols19]

nodecols19 <- c("Country", "Region", "Influenza2019")
nodes19 <- nodes19[nodecols19]

net_2019 <- graph_from_data_frame(d = links19, vertices = nodes19, directed=T) 
bc <- betweenness(net_2019, directed = TRUE)
dfbc19 <- data.frame(V1 = sort(bc, decreasing=TRUE))
names(dfbc19)[1]<-"Betweenness Centrality (2019)"
dfbc19
```



















