---
title: "UN Migration Data - Version 2"
author: "Winnie Hu"
date: "2/19/2020"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: show
always_allow_html: yes
autosize: True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
library(formattable)
library(ggplot2)
library(DT)
library(dplyr)
library(tidyr)
library(scales)
library(tibble)
library(networkD3)
library(visNetwork)
```

## Load Data

```{r q1, echo=TRUE}
setwd("C:/Users/Winnie/Documents/NeilJohnson/Migration")
nodes <- read.csv("CountryNodes.csv", header=T, as.is=T)
links <- read.csv("EdgeList.csv", header=T, as.is=T)
```

## Examine Data

### i) Nodes and Links

```{r q2, echo=FALSE}
head(nodes)
head(links)
no_country <- nrow(nodes)
no_region <- length(unique(nodes$Region))
unique_region <- unique(nodes$Region)
no_corridors <- nrow(links)
min_weight <- min(links$Weight)
max_weight <- max(links$Weight)

# Check whether country with special symbols in its name has been loaded successfully 
special_symbol <- nodes[170:175,]
special_symbol
```
The CountryNodes.csv file contains `r format(no_country)` countries and/or regions in the world. These countries are grouped into `r format(no_region)` regions, which are `r format(unique_region[-22])`, and `r format(unique_region[22])`. There are `r format(comma(no_corridors, digits = 0))` migration corridors in the EdgeList.csv file. The minimum weight is `r format(min_weight)`. The maximum weight is `r format(max_weight)`. 

### ii) Percentile

```{r q_percentile, echo=FALSE}
df_Weight_sort <- links[order(-links$Weight),]
quantilevalues <- quantile(df_Weight_sort$Weight, c(0.75, 0.80,  0.85, 0.95, 0.96, 0.97, 0.98, 0.99, 1))
quantilevalues
one_pct <- round(nrow(links)*0.01, 0)
```

The percentile values show that approximately 80% of the links are unweighted. Approximately 1 percent of the total links, equivalent to `r format(one_pct)` links, have migration flow greater than 79,680.  

### iii) Top migration corridors 

```{r q3, echo=FALSE}
df_desc <- links[order(-links$Weight),]
df_top_100 <- df_desc[1:100, ]
datatable(df_top_100)
```

### iv) Top migration destinations (coutries)

```{r q4, echo=FALSE}
top_dest <- aggregate(links$Weight, by=list(Destination = links$Destination), FUN = sum)
top_dest_desc <- top_dest[order(-top_dest$x),]
#top_20_dest <- top_dest_desc[1:20,]
datatable(top_dest_desc)
```

### v) Density

```{r q_dencity, echo=TRUE}
# remove links with 0 weight
links_wonly <-links[!(links$Weight==0),]
head(links_wonly)

# Create an igraph object
net <- graph_from_data_frame(d=links_wonly, vertices=nodes, directed=T) 

# directed network
no_edge <- ecount(net)
no_node <- vcount(net)
density_directed <- ecount(net)/(vcount(net)*(vcount(net)-1))
```

Density is the proportion of present edges from all possible edges in the network. Bsed on the density formular ecount(net)/(vcount(net)*(vcount(net)-1)) and knowing there are `r format(no_node)` nodes and `r format(no_edge)` edges, we derived that the network density for the migration dataset is `r format(density_directed)`. 

### vi) Reciprocity

```{r q_reciprocity, echo=TRUE}
# directed network
reciprocity_directed <- reciprocity(net)
```

Reciprocity is a measure of the likelihood of vertices to be mutually linked in a directed network. The reciprocity of the class network is `r format(reciprocity_directed)`.

## Visualization 

### 1.1 Explore different layouts

```{r q_alllinks, echo=TRUE}
# plot four figures - 2 rows, 2 columns
par(mfrow=c(2,2), mai=c(0.1, 0.1, 0.1, 0.1)) 

# make 4 subplots
# fr
plot(net, vertex.size=10, vertex.color="lightblue", edge.color="gray70", vertex.frame.color="SkyBlue2", edge.arrow.size=0.1, edge.width = (edge_attr(net)$weight)/1000000, vertex.label=NA, layout = layout_with_fr, main = "layout_with_fr")
# kk
plot(net, vertex.size=10, vertex.color="lightblue", edge.color="gray70", vertex.frame.color="SkyBlue2", edge.arrow.size=0.1, edge.width = (edge_attr(net)$weight)/1000000, vertex.label=NA, layout = layout_with_kk, main="layout_with_kk")
# circle
plot(net, vertex.size=10, vertex.color="lightblue", edge.color="gray70", vertex.frame.color="SkyBlue2", edge.arrow.size=0.1, edge.width = (edge_attr(net)$weight)/100000000, vertex.label=NA, layout = layout_in_circle, main="layout_in_circle")
#lgl
plot(net, vertex.size=10, vertex.color="lightblue", edge.color="gray70", vertex.frame.color="SkyBlue2", edge.arrow.size=0.1, edge.width = (edge_attr(net)$weight)/1000000, vertex.label=NA, layout = layout_with_lgl, main="layout_with_lgl")
```

### 1.2 Smart Questions
##### i) Degree analysis: What are the countries that are more open to migration? 

```{r q_degree, echo=TRUE}
# rescale the range of node weights to range of (0, 1)
links_wonly$Weight_rescale <- rescale(x = links_wonly$Weight, to = c(0, 1), from = range(x = links_wonly$Weight, na.rm = TRUE, finite = TRUE))
head(links_wonly)

#create igraph object
net_degree <- graph_from_data_frame(d=links_wonly, vertices=nodes, directed=T)

# get degree
deg <- degree(net_degree, mode='all')
deg_sort <- sort(x = deg, decreasing=TRUE)
col_deg <- data.frame(deg_sort) # covert vector to a dataframe
new_col_deg <- col_deg %>% rownames_to_column("Country") # convert rownames to a column refrence:https://rpubs.com/tuyenhavan/290871
colnames(new_col_deg) <- c("Country", "Degree") # reset column names
df_merge <- merge(nodes, new_col_deg) # merge two df based on common column "Country"
new_nodes <- df_merge[order(df_merge$Degree),] # sort the new df based on Degree in descending order
head(new_nodes, 10)
tail(new_nodes, 10)

###########
## Plot  ##
###########
# create new igraph object
net_degree2 <- graph_from_data_frame(d=links_wonly, vertices=new_nodes, directed=T)

# vertex color based on degree level
vcol <- rep("snow2", vcount(net_degree2))     #deebf7 # assigned third degree very light blue to top 101 - 232 countries
vcol[223:232] <- "skyblue1"                   #3182bd  #assign first degree dark blue to top ten countries
vcol[123:222] <- "slategray1"                 #9ecae1 #assign second degree light blue to top 11-100 countries
V(net_degree2)$color <- vcol

# vertex frame color
V(net_degree2)$frame.color <- "black"

# vertex label and size
V(net_degree2)$label <- new_nodes$Country
V(net_degree2)$label.cex <- 0.5
V(net_degree2)$label.color <- "white"

# Vertex size
V(net_degree2)$size <- round((new_nodes$Degree)/16, 2)

# edge color and size
E(net_degree2)$width <- links_wonly$Weight_rescale
E(net_degree2)$color <- "gray80"
E(net_degree2)$arrow.size <- .2
#E(net_degree)$arrow.mode <- 1

# layout
l <- layout_with_fr(net_degree2)

# plot
par(mai=c(0,0,0.1,0.1))
plot(net_degree2, layout = l, vertex.label = ifelse(degree(net_degree2) > 300, V(net_degree2)$label, NA), main="Network Graph based on Node Degree")
#legend("topleft", legend=c("a", "b", "c"), col=c("snow2", "skyblue1", "slategray1"), lty=1:2, cex=0.8)
```


```{r q_network3D, echo=TRUE}
nodes_vis <- new_nodes
colnames(nodes_vis) <- c("id", "group", "Degree")
head(nodes_vis)

edges_vis <- links_wonly[, c("Destination", "Origin", "Weight_rescale")]
colnames(edges_vis) <- c("to", "from", "weight")
head(edges_vis)

visNetwork(nodes_vis, edges_vis) %>% 
  visIgraphLayout(layout = "layout_with_fr")  %>% 
  visLegend()

```






































