---
title: "UN Migration Data - Version 7"
author: "Winnie Hu"
date: "3/24/2020"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: show
always_allow_html: yes
autosize: True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
library(formattable)
library(ggplot2)
library(DT)
library(dplyr)
library(tidyr)
library(scales)
library(tibble)
library(networkD3)
library(visNetwork)
```

# Load Data

```{r q1, echo=TRUE}
setwd("C:/Users/Winnie/Documents/NeilJohnson/Migration/Version_6_March_24")
nodes <- read.csv("CountryNodes_All.csv", header=T, as.is=T)
links <- read.csv("EdgeList_All.csv", header=T, as.is=T)
```

# Examine Data

## i) Nodes and Links

```{r q2, echo=FALSE}
nodes
links
```


# Plot

## i) rescale all links and node sizes across all yearly data

```{r plot_rescale, echo=TRUE}
### rescale the node size across all yearly data
# select columns for forming the new nodes df
columnsforts <- c("Country", "Country", "UN_Region", "Influenza2005", "Influenza2010",  "Influenza2015",  "Influenza2019")
nodes_ts <- nodes[columnsforts]
names(nodes_ts)[2] <- "Label" # rename "country.1" to "Country_Name_Label"
#nodes_ts

# recale the entire nodes df
# find the largest and smallest nodes value
colMax <- function(data) sapply(data, max, na.rm = TRUE)
#colMax(nodes_ts)
colMin <- function(data) sapply(data, min, na.rm = TRUE)
#colMin(nodes_ts)
# rescale the entire time series nodes df
# 2019
nodes_ts$Rescale_Inf2019 <- rescale(x = nodes_ts$Influenza2019, to = c(5, 28), from = range(x = nodes_ts$Influenza2019), na.rm = TRUE, finite = TRUE)
# 2015
nodes_ts$Rescale_Inf2015 <- rescale(x = nodes_ts$Influenza2015, to = c(5, 28), from = range(x = nodes_ts$Influenza2019), na.rm = TRUE, finite = TRUE)
# 2010
nodes_ts$Rescale_Inf2010 <- rescale(x = nodes_ts$Influenza2010, to = c(5, 28), from = range(x = nodes_ts$Influenza2019), na.rm = TRUE, finite = TRUE)
# 2005
nodes_ts$Rescale_Inf2005 <- rescale(x = nodes_ts$Influenza2005, to = c(5, 28), from = range(x = nodes_ts$Influenza2019), na.rm = TRUE, finite = TRUE)
#nodes_ts

### create links df for each year
# 2019
colsts2019 <- c("Origin", "Destination", "increase_rate_2015_2019")
links_ts_2019 <- links[colsts2019]
# remove links with 0 weight and negative weight
links_ts_2019 <-links_ts_2019[!(links_ts_2019$increase_rate_2015_2019 == 0),]
links_ts_2019 <-links_ts_2019[!(links_ts_2019$increase_rate_2015_2019 < 0),]
# rescale links width across all four years' data
links_ts_2019$Rescale_link_width <- rescale(x = links_ts_2019$increase_rate_2015_2019, to = c(0.2, 2), from = range(x = links_ts_2005$increase_rate_2000_2005), na.rm = TRUE, finite = TRUE) # the largest increase rate was 167800 in 2005 

# 2015
colsts2015 <- c("Origin", "Destination", "increase_rate_2010_2015")
links_ts_2015 <- links[colsts2015]
# remove links with 0 weight and negative weight
links_ts_2015 <-links_ts_2015[!(links_ts_2015$increase_rate_2010_2015 == 0),]
links_ts_2015 <-links_ts_2015[!(links_ts_2015$increase_rate_2010_2015 < 0),]
# rescale links width across all four years' data
links_ts_2015$Rescale_link_width <- rescale(x = links_ts_2015$increase_rate_2010_2015, to = c(0.2, 2), from = range(x = links_ts_2005$increase_rate_2000_2005), na.rm = TRUE, finite = TRUE)

# 2010
colsts2010 <- c("Origin", "Destination", "increase_rate_2005_2010")
links_ts_2010 <- links[colsts2010]
# remove links with 0 weight and negative weight
links_ts_2010 <-links_ts_2010[!(links_ts_2010$increase_rate_2005_2010 == 0),]
links_ts_2010 <-links_ts_2010[!(links_ts_2010$increase_rate_2005_2010 < 0),]
# rescale links width across all four years' data
links_ts_2010$Rescale_link_width <- rescale(x = links_ts_2010$increase_rate_2005_2010, to = c(0.2, 2), from = range(x = links_ts_2005$increase_rate_2000_2005), na.rm = TRUE, finite = TRUE)

# 2005
colsts2005 <- c("Origin", "Destination", "increase_rate_2000_2005")
links_ts_2005 <- links[colsts2005]
# remove links with 0 weight and negative weight
links_ts_2005 <-links_ts_2005[!(links_ts_2005$increase_rate_2000_2005 == 0),]
links_ts_2005 <-links_ts_2005[!(links_ts_2005$increase_rate_2000_2005 < 0),]
# rescale links width across all four years' data
links_ts_2005$Rescale_link_width <- rescale(x = links_ts_2005$increase_rate_2000_2005, to = c(0.2, 2), from = range(x = links_ts_2005$increase_rate_2000_2005), na.rm = TRUE, finite = TRUE)


# reference: find the max of a df https://stackoverflow.com/questions/10997444/how-to-find-highest-value-in-a-data-frame/38958839

```

## ii) plot 2005 - 2019: select links that immigration increase rate is greater than X%


```{r q_plot_2019_1, echo=TRUE}
# 2019
# select rows where the increase rate is > 50% of the data
links_19_greater_than_x_pct <- links_ts_2019[links_ts_2019$increase_rate_2015_2019 > 300, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2019
# create igraph object
net_19_links_greater_than_x_pct <- graph_from_data_frame(d=links_19_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_19_links_greater_than_x_pct)$size <- V(net_19_links_greater_than_x_pct)$Rescale_Inf2019

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2") 
my_color <- colrs[as.numeric(as.factor(V(net_19_links_greater_than_x_pct)$UN_Region))]
V(net_19_links_greater_than_x_pct)$color <- my_color
V(net_19_links_greater_than_x_pct)$frame.color <- "white"
V(net_19_links_greater_than_x_pct)$frame.size <- 0.1


V(net_19_links_greater_than_x_pct)$label.color <- 'black'
V(net_19_links_greater_than_x_pct)$label <- V(net_19_links_greater_than_x_pct)$Label
V(net_19_links_greater_than_x_pct)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_19_links_greater_than_x_pct)$width <- E(net_19_links_greater_than_x_pct)$Rescale_link_width

# set arrow size and edge color
E(net_19_links_greater_than_x_pct)$arrow.size <- 0.03
E(net_19_links_greater_than_x_pct)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_links_greater_than_300_pct_2019_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2019
plot(net_19_links_greater_than_x_pct, layout = layout_with_fr, main = "2019: Migration Increase Rate Greater Than 300%")

dev.off()

```

```{r q_plot_2015, echo=TRUE}

# select rows where the increase rate is > 50% of the data
links_15_greater_than_x_pct <- links_ts_2015[links_ts_2015$increase_rate_2010_2015 > 300, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2015
# create igraph object
net_15_links_greater_than_x_pct <- graph_from_data_frame(d=links_15_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_15_links_greater_than_x_pct)$size <- V(net_15_links_greater_than_x_pct)$Rescale_Inf2015

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2") 
my_color <- colrs[as.numeric(as.factor(V(net_15_links_greater_than_x_pct)$UN_Region))]
V(net_15_links_greater_than_x_pct)$color <- my_color
V(net_15_links_greater_than_x_pct)$frame.color <- "white"
V(net_15_links_greater_than_x_pct)$frame.size <- 0.1


V(net_15_links_greater_than_x_pct)$label.color <- 'black'
V(net_15_links_greater_than_x_pct)$label <- V(net_15_links_greater_than_x_pct)$Label
V(net_15_links_greater_than_x_pct)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_15_links_greater_than_x_pct)$width <- E(net_15_links_greater_than_x_pct)$Rescale_link_width

# set arrow size and edge color
E(net_15_links_greater_than_x_pct)$arrow.size <- 0.03
E(net_15_links_greater_than_x_pct)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_links_greater_than_300_pct_2015_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2019
plot(net_15_links_greater_than_x_pct, layout = layout_with_fr, main = "2015: Migration Increase Rate Greater Than 300%")

dev.off()

```

```{r q_plot_2010, echo=TRUE}

# select rows where the increase rate is > 50% of the data
links_10_greater_than_x_pct <- links_ts_2010[links_ts_2010$increase_rate_2005_2010 > 300, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2010
# create igraph object
net_10_links_greater_than_x_pct <- graph_from_data_frame(d=links_10_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_10_links_greater_than_x_pct)$size <- V(net_10_links_greater_than_x_pct)$Rescale_Inf2010

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2") 
my_color <- colrs[as.numeric(as.factor(V(net_10_links_greater_than_x_pct)$UN_Region))]
V(net_10_links_greater_than_x_pct)$color <- my_color
V(net_10_links_greater_than_x_pct)$frame.color <- "white"
V(net_10_links_greater_than_x_pct)$frame.size <- 0.1


V(net_10_links_greater_than_x_pct)$label.color <- 'black'
V(net_10_links_greater_than_x_pct)$label <- V(net_10_links_greater_than_x_pct)$Label
V(net_10_links_greater_than_x_pct)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_10_links_greater_than_x_pct)$width <- E(net_10_links_greater_than_x_pct)$Rescale_link_width

# set arrow size and edge color
E(net_10_links_greater_than_x_pct)$arrow.size <- 0.03
E(net_10_links_greater_than_x_pct)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_links_greater_than_300_pct_2010_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2010
plot(net_10_links_greater_than_x_pct, layout = layout_with_fr, main = "2010: Migration Increase Rate Greater Than 300%")

dev.off()

```

```{r q_plot_2005, echo=TRUE}

# select rows where the increase rate is > 50% of the data
links_05_greater_than_x_pct <- links_ts_2005[links_ts_2005$increase_rate_2000_2005 > 300, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2005
# create igraph object
net_05_links_greater_than_x_pct <- graph_from_data_frame(d=links_05_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_05_links_greater_than_x_pct)$size <- V(net_05_links_greater_than_x_pct)$Rescale_Inf2005

# node color
library(RColorBrewer)
colrs  <- brewer.pal(7, "Set2") 
my_color <- colrs[as.numeric(as.factor(V(net_05_links_greater_than_x_pct)$UN_Region))]
V(net_05_links_greater_than_x_pct)$color <- my_color
V(net_05_links_greater_than_x_pct)$frame.color <- "white"
V(net_05_links_greater_than_x_pct)$frame.size <- 0.1


V(net_05_links_greater_than_x_pct)$label.color <- 'black'
V(net_05_links_greater_than_x_pct)$label <- V(net_05_links_greater_than_x_pct)$Label
V(net_05_links_greater_than_x_pct)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_05_links_greater_than_x_pct)$width <- E(net_05_links_greater_than_x_pct)$Rescale_link_width

# set arrow size and edge color
E(net_05_links_greater_than_x_pct)$arrow.size <- 0.03
E(net_05_links_greater_than_x_pct)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_links_greater_than_300_pct_2005_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2005
plot(net_05_links_greater_than_x_pct, layout = layout_with_fr, main = "2005: Migration Increase Rate Greater Than 300%")

dev.off()

```

## iii) plot 2005 - 2019: select links that immigration increase rate is greater than X% & highlight nodes with different color

In this section, nodes with largest influenza data are colored by gold. nodes with largest node degree are colored by blue. Nodes that are both largest indluenza country and largest node degree use red. Other nodes are colored in grey.

### i) create a new feature in the country node csv that is used to record the node color.
```{r q_plot_3_1, echo=TRUE}
#### 2019
### get the top 10 countries that have the largest influenza cases in 2019
top_IC_19 <- nodes_ts[order(-nodes_ts$Influenza2019),]$Country[1:10]
top_IC_19

### get the top 10 countries that have the largest node degree in 2019
# select rows where the increase rate is > X% of the data
links_19_greater_than_x_pct <- links_ts_2019[links_ts_2019$increase_rate_2015_2019 > 200, ]
# create igraph object
net_19_links_greater_than_x_pct <- graph_from_data_frame(d=links_19_greater_than_x_pct, vertices = nodes_ts, directed=T)
#deg_19 <- degree(net_19_links_greater_than_x_pct, mode="in")
top_ND_19 <- sort(degree(net_19_links_greater_than_x_pct, mode="in"), decreasing = TRUE)[1:10] # careful with in and out.
top_ND_19
sequence <- c(1, 2, 3, 4, 5, 6, 7, 10)
top_NDL_19 <- vector()
for (val in sequence){
  top_NDL_19 <- c(top_NDL_19, V(net_19_links_greater_than_x_pct)$Label[degree(net_19_links_greater_than_x_pct, mode = 'in') == top_ND_19[val]])
}
#top_NDL_19

# get the nodes that are in both top_IR and top_NDL
top_both_19 <- intersect(top_IC_19, top_NDL_19)
top_both_19

### assign color lables 
# Others
nodes_ts$Node_Color_19 <- "Others"
# top countries by influenza cases
for (val in top_IC_19){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_19 <- "Top Countries by influenza cases"
}
# top countries by in-node degree (number of links that have migration increase rate greater than X%)
for (val in top_NDL_19){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_19 <- "Top Countries by in-node degree" 
}
# top countries by both
for (val in top_both_19){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_19 <- "Top Countries that met both criteria" 
}
#nodes_ts
```

```{r q_plot_3_2, echo=TRUE}
# 2019
# select rows where the increase rate is > X% of the data
links_19_greater_than_x_pct <- links_ts_2019[links_ts_2019$increase_rate_2015_2019 > 200, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2019
# create igraph object
net_19_color <- graph_from_data_frame(d=links_19_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_19_color)$size <- V(net_19_color)$Rescale_Inf2019

# node color
#library(RColorBrewer)
#colrs  <- brewer.pal(4, "Set2") 
colrs <- c("grey80", "gold", "blue", "red")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_19_color)$Node_Color_19))]
V(net_19_color)$color <- my_color
V(net_19_color)$frame.color <- "white"
V(net_19_color)$frame.size <- 0.1


V(net_19_color)$label.color <- 'black'
V(net_19_color)$label <- V(net_19_color)$Label
V(net_19_color)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_19_color)$width <- E(net_19_color)$Rescale_link_width

# set arrow size and edge color
E(net_19_color)$arrow.size <- 0.03
E(net_19_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_node_color_2019_200_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2019
plot(net_19_color, layout = layout_with_fr, main = "2019: Migration Increase Rate Greater Than 200% (fr)")

dev.off()

# reference: color transparency http://www.kateto.net/wp-content/uploads/2016/04/Sunbelt%202016%20R%20Network%20Visualization%20Handout.pdf
```

```{r q_plot_3_2015, echo=TRUE}
#### 2015
### get the top 10 countries that have the largest influenza cases in 2015
top_IC_15 <- nodes_ts[order(-nodes_ts$Influenza2015),]$Country[1:10]
top_IC_15

### get the top 10 countries that have the largest node degree in 2015
# select rows where the increase rate is > X% of the data
links_15_greater_than_x_pct <- links_ts_2015[links_ts_2015$increase_rate_2010_2015 > 200, ]
# create igraph object
net_15_links_greater_than_x_pct <- graph_from_data_frame(d=links_15_greater_than_x_pct, vertices = nodes_ts, directed=T)
# get top nodes
top_ND_15 <- sort(degree(net_15_links_greater_than_x_pct, mode="in"), decreasing = TRUE)[1:10] # careful with in and out.
top_ND_15

sequence <- c(1, 2, 3, 4, 6, 8, 10)
top_NDL_15 <- vector()
for (val in sequence){
  top_NDL_15 <- c(top_NDL_15, V(net_15_links_greater_than_x_pct)$Label[degree(net_15_links_greater_than_x_pct, mode = 'in') == top_ND_15[val]])
}
top_NDL_15

# get the nodes that are in both top_IR and top_NDL
top_both_15 <- intersect(top_IC_15, top_NDL_15)
top_both_15

### assign color lables 
# Others
nodes_ts$Node_Color_15 <- "Others"
# top countries by influenza cases
for (val in top_IC_15){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_15 <- "Top Countries by influenza cases"
}
# top countries by in-node degree (number of links that have migration increase rate greater than X%)
for (val in top_NDL_15){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_15 <- "Top Countries by in-node degree" 
}
# top countries by both
for (val in top_both_15){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_15 <- "Top Countries that met both criteria" 
}
#nodes_ts


# select rows where the increase rate is > X% of the data
links_15_greater_than_x_pct <- links_ts_2015[links_ts_2015$increase_rate_2010_2015 > 200, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2015
# create igraph object
net_15_color <- graph_from_data_frame(d=links_15_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_15_color)$size <- V(net_15_color)$Rescale_Inf2015

# node color
#library(RColorBrewer)
#colrs  <- brewer.pal(4, "Set2") 
colrs <- c("grey80", "gold", "blue", "red")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_15_color)$Node_Color_15))]
V(net_15_color)$color <- my_color
V(net_15_color)$frame.color <- "white"
V(net_15_color)$frame.size <- 0.1


V(net_15_color)$label.color <- 'black'
V(net_15_color)$label <- V(net_19_color)$Label
V(net_15_color)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_15_color)$width <- E(net_15_color)$Rescale_link_width

# set arrow size and edge color
E(net_15_color)$arrow.size <- 0.03
E(net_15_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_node_color_2015_200_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2019
plot(net_15_color, layout = layout_with_fr, main = "2015: Migration Increase Rate Greater Than 200% (fr)")

dev.off()
```

```{r q_plot_3_2010, echo=TRUE}
#### 2010
### get the top 10 countries that have the largest influenza cases in 2010
top_IC_10 <- nodes_ts[order(-nodes_ts$Influenza2010),]$Country[1:10]
top_IC_10

### get the top 10 countries that have the largest node degree in 2015
# select rows where the increase rate is > X% of the data
links_10_greater_than_x_pct <- links_ts_2010[links_ts_2010$increase_rate_2005_2010 > 200, ]
# create igraph object
net_10_links_greater_than_x_pct <- graph_from_data_frame(d=links_10_greater_than_x_pct, vertices = nodes_ts, directed=T)
# get top nodes
top_ND_10 <- sort(degree(net_10_links_greater_than_x_pct, mode="in"), decreasing = TRUE)[1:10] # careful with in and out.
top_ND_10

#sequence <- c(1, 2, 3, 4, 5, 7, 10)
sequence <- c(1, 3, 5, 8, 9)

top_NDL_10 <- vector()
for (val in sequence){
  top_NDL_10 <- c(top_NDL_10, V(net_10_links_greater_than_x_pct)$Label[degree(net_10_links_greater_than_x_pct, mode = 'in') == top_ND_10[val]])
}
#top_NDL_19

# get the nodes that are in both top_IR and top_NDL
top_both_10 <- intersect(top_IC_10, top_NDL_10)
top_both_10

### assign color lables 
# Others
nodes_ts$Node_Color_10 <- "Others"
# top countries by influenza cases
for (val in top_IC_10){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_10 <- "Top Countries by influenza cases"
}
# top countries by in-node degree (number of links that have migration increase rate greater than X%)
for (val in top_NDL_10){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_10 <- "Top Countries by in-node degree" 
}
# top countries by both
for (val in top_both_10){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_10 <- "Top Countries that met both criteria" 
}
#nodes_ts


# select rows where the increase rate is > X% of the data
links_10_greater_than_x_pct <- links_ts_2010[links_ts_2010$increase_rate_2005_2010 > 200, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2010
# create igraph object
net_10_color <- graph_from_data_frame(d=links_10_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_10_color)$size <- V(net_10_color)$Rescale_Inf2010

# node color
#library(RColorBrewer)
#colrs  <- brewer.pal(4, "Set2") 
colrs <- c("grey80", "gold", "blue", "red")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_10_color)$Node_Color_10))]
V(net_10_color)$color <- my_color
V(net_10_color)$frame.color <- "white"
V(net_10_color)$frame.size <- 0.1


V(net_10_color)$label.color <- 'black'
V(net_10_color)$label <- V(net_10_color)$Label
V(net_10_color)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_10_color)$width <- E(net_10_color)$Rescale_link_width

# set arrow size and edge color
E(net_10_color)$arrow.size <- 0.03
E(net_10_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_node_color_2010_200_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2010
plot(net_10_color, layout = layout_with_fr, main = "2010: Migration Increase Rate Greater Than 200% (fr)")

dev.off()
```


```{r q_plot_3_2005, echo=TRUE}
#### 2005
### get the top 10 countries that have the largest influenza cases in 2010
top_IC_05 <- nodes_ts[order(-nodes_ts$Influenza2005),]$Country[1:10]
top_IC_05

### get the top 10 countries that have the largest node degree in 2015
# select rows where the increase rate is > X% of the data
links_05_greater_than_x_pct <- links_ts_2005[links_ts_2005$increase_rate_2000_2005 > 200, ]
# create igraph object
net_05_links_greater_than_x_pct <- graph_from_data_frame(d=links_05_greater_than_x_pct, vertices = nodes_ts, directed=T)
# get top nodes
top_ND_05 <- sort(degree(net_05_links_greater_than_x_pct, mode="in"), decreasing = TRUE)[1:10] # careful with in and out.
top_ND_05

#sequence <- c(1, 2, 3, 4, 5, 6, 7, 9)
sequence <- c(1, 2, 3, 4, 5, 6, 7, 8, 9)
top_NDL_05 <- vector()
for (val in sequence){
  top_NDL_05 <- c(top_NDL_05, V(net_05_links_greater_than_x_pct)$Label[degree(net_05_links_greater_than_x_pct, mode = 'in') == top_ND_05[val]])
}
#top_NDL_05

# get the nodes that are in both top_IR and top_NDL
top_both_05 <- intersect(top_IC_05, top_NDL_05)
top_both_05

### assign color lables 
# Others
nodes_ts$Node_Color_05 <- "Others"
# top countries by influenza cases
for (val in top_IC_05){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_05 <- "Top Countries by influenza cases"
}
# top countries by in-node degree (number of links that have migration increase rate greater than X%)
for (val in top_NDL_05){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_05 <- "Top Countries by in-node degree" 
}
# top countries by both
for (val in top_both_05){
  nodes_ts[nodes_ts$Country == val,]$Node_Color_05 <- "Top Countries that met both criteria" 
}
#nodes_ts


# select rows where the increase rate is > X% of the data
links_05_greater_than_x_pct <- links_ts_2005[links_ts_2005$increase_rate_2000_2005 > 200, ]

# set figure size
par(pin=c(5, 4))
par(mai=c(0.1, 0.1, 0.2, 0.1))

# 2010
# create igraph object
net_05_color <- graph_from_data_frame(d=links_05_greater_than_x_pct, vertices = nodes_ts, directed=T)

# node size
V(net_05_color)$size <- V(net_05_color)$Rescale_Inf2005

# node color
#library(RColorBrewer)
#colrs  <- brewer.pal(4, "Set2") 
colrs <- c("grey80", "gold", "blue", "red")
colrstr <- grDevices::adjustcolor(colrs, alpha=0.4)
my_color <- colrstr[as.numeric(as.factor(V(net_05_color)$Node_Color_05))]
V(net_05_color)$color <- my_color
V(net_05_color)$frame.color <- "white"
V(net_05_color)$frame.size <- 0.1


V(net_05_color)$label.color <- 'black'
V(net_05_color)$label <- V(net_10_color)$Label
V(net_05_color)$label.cex = 0.15
#vertex.label.family="sans"

# edge
# set edge width
E(net_05_color)$width <- E(net_05_color)$Rescale_link_width

# set arrow size and edge color
E(net_05_color)$arrow.size <- 0.03
E(net_05_color)$arrow.mode <- 2 # 2 for forward arrow from Origin to Destination (1 for backward) 

# set seed
set.seed(1234)

jpeg("Figure_node_color_2005_200_fr.jpg", width=10, height=6, units='in',res=1000)

# plot 2010
plot(net_05_color, layout = layout_with_fr, main = "2005: Migration Increase Rate Greater Than 200% (fr)")

dev.off()
```























































