---
title: "UN Migration Data"
author: "Winnie Hu"
date: "2/9/2020"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: show
always_allow_html: yes
autosize: True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
library(formattable)
library(ggplot2)
library(DT)
```

## Load Data

```{r q1, echo=TRUE}
setwd("C:/Users/Winnie/Documents/NeilJohnson/Migration")
nodes <- read.csv("CountryNodes.csv", header=T, as.is=T)
links <- read.csv("EdgeList.csv", header=T, as.is=T)
```

## Examine Data

```{r q2, echo=FALSE}
head(nodes)
head(links)
no_country <- nrow(nodes)
no_region <- length(unique(nodes$Region))
unique_region <- unique(nodes$Region)
no_corridors <- nrow(links)
```

The CountryNodes.csv file contains `r format(no_country)` countries and/or regions in the world. These countries are grouped into `r format(no_region)` regions, which are `r format(unique_region[-22])`, and `r format(unique_region[22])`. There are `r format(comma(no_corridors, digits = 0))` migration corridors in the EdgeList.csv file.

## Exploratory Data Analysis

### 1. Top migration corridors 

```{r q3, echo=FALSE}
df_desc <- links[order(-links$Weight),]
df_top_100 <- df_desc[1:100, ]
datatable(df_top_100)
```

### 2. Top migration destinations (coutries)

```{r q4, echo=FALSE}
top_dest <- aggregate(links$Weight, by=list(Destination = links$Destination), FUN = sum)
top_dest_desc <- top_dest[order(-top_dest$x),]
#top_20_dest <- top_dest_desc[1:20,]
datatable(top_dest_desc)
```

## Visualization 

### 1.1 All links

```{r q5, echo=FALSE}
# Create igraph object
net_all <- graph_from_data_frame(d=links, vertices=nodes, directed = F)

# set attributes parameters
V(net_all)$size <- 8
V(net_all)$frame.color <- "white"
V(net_all)$color <- "lightblue"
V(net_all)$label.color <- "grey"
V(net_all)$label <- nodes$Country
V(net_all)$label.dist <- 1
E(net_all)$arrow.size <- 0.1
E(net_all)$width <- (edge_attr(net_all)$Weight)/1000000

# Set layout
graph_attr(net_all, "layout") <- layout_with_lgl

# Plot
plot(net_all)
```

### 1.2 All links with modifications

```{r q6, echo=FALSE}
# Create igraph object
net_all2 <- graph_from_data_frame(d=links, vertices=nodes, directed = F)

# set attributes parameters
V(net_all)$frame.color <- "white"
V(net_all)$color <- "lightblue"
V(net_all)$label <- NA
E(net_all)$width <- (edge_attr(net_all)$Weight)/100000000

# Set node size based on migration total individuals
V(net_all)$size <- (top_dest$x)/1000000

# Set layout
graph_attr(net_all, "layout") <- layout_in_circle

# Plot
plot(net_all)
```



### 2.1 Only top 20 corridors

```{r q7, echo=FALSE}
# subset 
df_top_20_corridors <- df_desc[1:20, ]

# Create igraph object
net_all_20 <- graph_from_data_frame(d=df_top_20_corridors, vertices=nodes, directed = F)

# set attributes parameters
V(net_all_20)$frame.color <- "white"
V(net_all_20)$color <- "lightblue"
V(net_all_20)$label <- NA
E(net_all_20)$width <- (edge_attr(net_all_20)$Weight)/1000000

# Set node size based on migration total individuals
V(net_all_20)$size <- (top_dest$x)/1000000

# Set layout
graph_attr(net_all_20, "layout") <- layout_in_circle

# Plot
plot(net_all_20)
```











































